r5r: Rapid Realistic Routing with R5 in R

### 2020-09-15 r-package/paper2020/paper2020.Rmd
paper: 1st paragraph done

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly.

Despite the long standing importance of routing analysis to the field, transport 
researchers and practitioners still frequently face practical challenges with 
this task. These challenges involve for example the monetary costs of licensed 
software, data availability issues for data hungry models, and the long 
computation times to run multiple routing scenarios, particularly in large and 
complex multimodal transport networks. While there is a growing number of open source routing models (ref: stplnr, otp, dodgr), most options available only return the fastest route, what overlooks....

>>>>

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly. Despite the long-standing importance of routing analysis to the 
field, transport researchers and practitioners still frequently face practical 
challenges with this task. These challenges involve for example the monetary 
costs of licensed software, data availability issues for data hungry models, and
the long computation times to run multiple routing scenarios, particularly in 
large and complex multimodal transport networks. While there is a growing number
of open source routing models (ref: stplnr, otp, dodgr), most options available 
only return the fastest route option between a set of origins and destinations. 
This simple approach overlooks how often people's actual route choices deviate 
from shortest travel time paths due to imperfect information, monetary costs and
safety issues among other reasons (refs, 1 2 3).
Refs:
1 - https://tram.mcgill.ca/Research/Publications/Who_will_use_it.pdf
2 - https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0134322
3 - https://www.tandfonline.com/doi/abs/10.1080/13658816.2019.1605075
